\documentclass{screenplay}[2012/06/30]
\title{Boulders}
\author{Samuel Jurado}
\address{628 Eten \\
    CDMX \\ 07730 \\
    4646503231 \\
    samuelaljuma@gmail.com }

\begin{document}
\coverpage

\fadein

\extslug[day]{Army desert camp}
The sun is rising on the horizon as we see a bus driving
through the endless dunes, which fill the entire view
apart from the vestiges of the once great cities of the
desert . A pair of big black leather
boots blocks the view as the bus approaches the wearer.
As the bus arrives the passengers step
down from it and the camera focuses on the last one to do so.
He doesn't seem happy to be there, as opposed to the
other passengers which we can see grinning and rushing where
the wearer of the black boots is.

\begin{dialogue}[shouting]{Sergeant Seth}
    Hurry up soldiers! And welcome to your new home until you
    make us win the war or die trying!
\end{dialogue}

In an instant, all the soldiers form a horizontal line in front of the
Sergeant, except for the last one to come down of the bus, Colt.

\begin{dialogue}[Yelling to Colt]{Sergeant Seth}
    Didn't you hear me soldier? I said hurry up. I've got
    more important things to do than babysitting you, but we're
    short on staff, so I'm doing this quickly.
\end{dialogue}

Colt lines up in the dead center of the line, he hates to
be the center of attention so getting called out again would
be undesirable. Sergeant Seth paces back and forth through the line as he
talks.

\begin{dialogue}{Sergeant Seth}
    As you may know, the war we're fighting seems to be
    endless, and I'm not here to tell you some bullshit
    like you are the last hope of our country and so on. I know
    and you know you're here because of one of two reasons:
    You love to kill or you just didn't have anywhere else
    to go\dots
\end{dialogue}

The latter is the case for Colt. The Sergeant words rumble on
his head as the Sergeant continues to speak. A few moments
pass and Colt comes back on himself, but the Sergeant's speech
is already about to end.

\begin{dialogue}{Sergeant Seth}
    \dots In conclusion, because of our fruitless attempts
    to finish this war, the government has decided it's time
    to get experimental.
\end{dialogue}

The Sergeant points to several wooden crates that were
previously covered, revealing that they contain young
canines.

\begin{dialogue}{Sergeant Seth}
    Each one of you is going to be assigned a canine partner.
    This breed is specifically made for the desert environment.
    They are going to be your lifeline on your ongoing missions
    but you will have to gain their trust and respect.
\end{dialogue}

Colt reluctantly receives his new partner, he didn't signed
up for this. He never was good maintaining any kind of
relationship, and now he has to make a strong bond with an
animal for his own good.

\extslug[day]{Army Trainning facilities}
We see the soldiers training with their new partners. Colt
stares down at his with a worried expression.

\begin{dialogue}[Diligent but insecure]{Colt}
    Okay uhmmmm\dots sit down!, roll!, jump!
\end{dialogue}

His partner stares back at him and turns its head sideways
expressing confusion.

\begin{dialogue}[To himself]{Colt}
    Great. Now I'm stuck in here with a stupid animal
    that I don't even know how to communicate to. Maybe
    I'm the stupid one on that regard, everyone else
    seems to be getting along fine with their partners.
\end{dialogue}

Colt glances around and sees how his fellow soldiers are
making great progress towards training their partners. The
frustration wins him over and he decides to sit besides a near
boulder and buries his face on his hands.

\begin{dialogue}[To himself]{Colt}
    This is stupid, I should just give up and return home.
\end{dialogue}

Colt's partner walks up to him and softly licks his hand
then it proceeds to curl up between his feet.

\begin{dialogue}[To himself, happily]{Colt}
    Huh, seems you haven't given up on me as I did.
\end{dialogue}

Colt smiles honestly, no one ever stood by his side like
this animal did. Everyone, including himself, abandoned all
hope on him as soon as he failed once.

\begin{dialogue}{Colt}
    Now that I think about it, I haven't named you.
\end{dialogue}

Colt looks back at the boulder he is leaning on and an
idea crosses his mind

\begin{dialogue}{Colt}
    I've got it! Since you are going to give me support
    and I can lean on you, I'm going to name you: Boulder!
\end{dialogue}

Boulder stands up and barks joyful once he hears his new name.

\begin{dialogue}{Colt}
    Yeah, I like it too!.Now come, I'm going to try my best
    to seize the chance you gave me!
\end{dialogue}

Weeks pass, and Colt and Boulder's friendship grows strong
as they train together. They run through the dunes like no
other partners do, they help each other to cruise through the
debris of the destroyed desert cities and they do an excellent
job at protecting each others back.

\extslug[night]{Sergeant Seth's Office}
Colt enters the Sergeant's office, he is sitting in his desk
looking at a map of the region.

\begin{dialogue}{Colt}
    You wanted to see me Sergeant?
\end{dialogue}

\begin{dialogue}[Serious Tone]{Sergeant Seth}
    I'm going to be very straightforward, kid. I need to
    send you and your canine partner on a mission you might
    not get back
\end{dialogue}

\begin{dialogue}{Colt}
    I understand, but, may I ask, what mission?
\end{dialogue}

\begin{dialogue}[Serious Tone]{Sergeant Seth}
    I need you to infiltrate the enemy base and retrieve 
    a very important USB drive that our sources believe 
    it contains the next plans of attack of our enemies.
    We have been trying to intercept them over multiple 
    mediums without succeeding, now we think the reason is 
    they don't transmit it over any signal but physically.
\end{dialogue}

\begin{dialogue}{Colt}
    And why us?
\end{dialogue}

\begin{dialogue}[A bit ashamed]{Sergeant Seth}
    None of the other soldiers on the program
    have shown the level of 
    teamwork you and your partner have.
    We need to succeed on this one, this time you are
    really the last hope of our country.  
\end{dialogue}

Colt nods agreeing on the mission and the Sergeant begins 
to explain the details of it.

\extslug[night]{Colt and Boulder's Tent}
Colt begins to tie a not around the center pole of the 
tent and Boulder's collar. Colt has a frown on his face,
but tries to hide it in an effort to not worry Boulder.
An effort that's quickly interrupted by Boulder's keen eye.

\begin{dialogue}[Sad]{Colt}
    I can't really hide it from you, can I?. I'm going on
    a mission and I may not get back. I've got direct orders
    to take you with me, but it would be a shame to lose an 
    amazing soldier like you, wouldn't it?. Don't worry 
    about me, I've trained with the best.
\end{dialogue}

Colt walks to the exit of the tent and looks back to see
Boulder one last time.
\begin{dialogue}[Holding his tears]{Colt}
    Thanks for supporting me!
\end{dialogue}

Boulder whimpers as he sees his partner
walking away without him. The hours past and Colt does not 
return, but Boulder does not find peace waiting for him at 
the tent, so he starts nibbling nervously and rapidly at 
his leash until he breaks free. He begins to sniff in search 
of Colt's scent and, as soon as he finds it, he begins to run
at it.

\extslug[night]{Enemy Fort}
Boulder arrives at the enemy's Fort, he tracks down Colt's 
scent down to an obscure cellar. The entrance seems to be 
closed but there's a tiny ventilation port at one of the sides. 
Boulder uses some wooden crates to climb up and then he manages 
to sneak into the cellar.

\intslug[night]{Detention Cellar}
At the center of the cellar, tied to a metal chair and 
lighted by a harsh white light is Colt who is equally 
happy and angry to see Boulder there.

\begin{dialogue}[Whispering angry]{Colt}
    You stubborn dog! I thought I've told you to stay in the 
    tent!
\end{dialogue}

Boulder licks frantically Colt's face and then starts nibbling
on the ropes that tie him.

\begin{dialogue}[Whispering]{Colt}
    Hurry up partner, it's a matter of time before they 
    figure out what I've stolen from them and\dots Shit! 
    They're coming, hide somewhere!.
\end{dialogue}

Boulder squeezes himself behind some barrels and Colt tucks 
his hand behind his back to pretend he is still tied. Some 
kind of officer, and two guards, enter the cellar speaking an unintelligible
language, nonetheless by the tone of their voice is very clear 
that they are not happy. The officer begins to yell at Colt and beats him up.
At that point Boulder jumps from his hiding spot and trows 
himself against the officer's face. 

\begin{dialogue}{Colt}
    Good job Boulder! But I've would have liked to have some
    kind of signal
\end{dialogue}

Colt uses the confusion to disarm and neutralize the guards.
When all seems settled Colt reaches his pocket and draws the 
USB to his hand.

\begin{dialogue}[Panting]{Colt}
    We did it partner!. Well, you did it. I would still be
    tied to that chair if it wasn't for you. Take care of 
    this for me, I want everybody to know who is the hero 
    that ended the war.
\end{dialogue}

Colt pats Boulders head and signals him to go ahead to watch 
out for more guards. After doing so he began to inspect the 
guards and Officer in search for weapons and ammo. Then, a 
dim beeping sound starts. Colt knows exactly what's happening.
He quickly reaches the cellar door and takes a good last look
at his best friend, the one he didn't wanted but certainly needed, 
as he closes the cellar door to protect Boulder from the explosion.

The explosion does not reach Boulder, he seems astonished 
to what is happening and his sadness is immense, but his 
best friend gave him an order and is his duty to honor that.
He turns around and rushes back to the army camp, before 
anyone sees what happened.

\intslug[day]{Army Camp}

Boulder arrives at the camp, visibly tired and with a loss 
look on his face. Sergeant Seth receives him and gently pats
his back.

\begin{dialogue}{Sergeant Seth}
    Rest now, Soldier, you have done enough.
\end{dialogue}

Hearing this words, Boulder curls up as he used to do at 
Colt's feet and deeply inhales his last breath. Apparently
some metal fragments managed to get to his stomach but 
that didn't stop him from fulfilling his mission. Now he can 
rest besides his partner and best friend.

According to Sergeant Seth's report, the information retrieved
from the USB was crucial for winning the war. The canine partner
project became known all around the country as also did the 
heroes who helped terminate the war. Now their bravery, compromise
and friendship is immortalized somewhere on a main square, in the 
newly revitalized country on the form of a statue of both of them.

\fadeout
\theend

\end{document}